Supplementary Material for Asymmetry paper

### 2020-06-08 Supplementary/Sup_mat.Rmd
More detail to 3.2

## Experiment 2: Two Throws
```{r Two Throws: load data, include = F, echo = F}
load("../Analyses/Experiment_2_Two_throw/scratch/model_data_pos")

@@

```{r Two_Throws_Priors_only_model, include = F, echo = F, cache = T}
Two_throw_priors <- brm(abspos ~ norm_delta * Num_throws + (norm_delta * Num_throws|Participant),
                        family = "beta",
                        data = model_data_pos,
                        prior = c(set_prior("student_t(4,0,.8)",
                                            class = "b",
                                            coef = "norm_delta"),
                                  set_prior("student_t(4,0,.8)",
                                            class = "b",
                                            coef = "norm_delta:Num_throwsTwoMThrows"),
                                  set_prior("student_t(4,0,.8)",
                                            class = "b", coef = "Num_throwsTwoMThrows"),
                                  set_prior("student_t(4,0,.8)",
                                            class = "Intercept")),
                        cores = 1,
                        chains = 1,
                        iter = 10000,
                        warmup = 5000,
                        control = list(adapt_delta = .99, max_treedepth = 15),
                        sample_prior = "only")

@@

priors_plt <- draws_df$Draws_df %>% 
  mutate(prop = boot::inv.logit(estimate)) %>% 
  ggplot(aes(prop, 
             colour = Num_throws,
             fill = Num_throws)) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  geom_density(
    kernel = "biweight",
    alpha = .3
  )+ 
  facet_wrap(~Dist_type) + 
  theme_bw()
```

@@

```{r Two-throws modelling, include = F, echo = F, cache = T}
Two_throw_m1 <- brm(abspos ~ norm_delta * Num_throws + (norm_delta * Num_throws|Participant),
                    family = "beta",
                    data = model_data_pos,
                    prior = c(set_prior("student_t(4,0,.8)",
                                        class = "b",
                                        coef = "norm_delta"),
                              set_prior("student_t(4,0,.8)",
                                        class = "b",
                                        coef = "norm_delta:Num_throwsTwoMThrows"),
                              set_prior("student_t(4,0,.8)",
                                        class = "b", coef = "Num_throwsTwoMThrows"),
                              set_prior("student_t(4,0,.8)",
                                        class = "Intercept")),
                    cores = 1,
                    chains = 1,
                    iter = 10000,
                    warmup = 5000,
                    control = list(adapt_delta = .99, max_treedepth = 15))

@@

```{r PltTwoThrowEstimates, include = T, echo = F, fig.asp=.55, fig.cap="_The top plots show the Posterior distributions for the estimated mean standing position. The bottom plot shows the distribution of estimated difference between the two conditions for three difference distances_"}
# example distributions 
plt_examples <- draws$Plots[1][[1]][["data"]] %>% 
  mutate(Dist_Type = factor(Dist_type, c("Close", "Mid", "Far")),
         Num_Throws = ifelse(Num_throws == "One_throw", "One", "Two")) %>% 
  ggplot(aes(prop, 
             colour = Num_Throws,
             fill = Num_Throws)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  facet_wrap(~Dist_Type) + 
  theme_bw() + 
  scale_x_continuous(expression(Delta)) + 
  coord_cartesian(expand = F) + 
  guides(fill = guide_legend(title = "No. Throws"),
         colour = guide_legend(title = "No. Throws"))

>>>>

```{r Two Throws: load data, include = F, echo = F}
load("../Analyses/Experiment_2_Two_throw/scratch/model_data_pos")

@@

We first carry out a prior predictive check to confirm that our choice of priors are reasonable.

```{r Two_Throws_Priors_only_model, include = F, echo = F, cache = T}

my_prior <- c(
  set_prior("student_t(4,0,.8)", class = "b", coef = "norm_delta"),
  set_prior("student_t(4,0,.8)", class = "b", coef = "norm_delta:Num_throwsTwoMThrows"),
  set_prior("student_t(4,0,.8)", class = "b", coef = "Num_throwsTwoMThrows"),
  set_prior("student_t(4,0,.8)", class = "Intercept"))

Two_throw_priors <- brm(
  abspos ~ norm_delta * Num_throws + (norm_delta * Num_throws|Participant),
  family = "beta",
  data = model_data_pos,
  prior = my_prior,
  cores = 1,
  chains = 1,
  iter = 10000,
  warmup = 5000,
  control = list(adapt_delta = .99, max_treedepth = 15),
  sample_prior = "only")

@@

priors_plt <- draws_df$Draws_df %>% 
  mutate(prop = boot::inv.logit(estimate)) %>% 
  ggplot(aes(prop,colour = Num_throws, fill = Num_throws)) + 
    see::scale_color_flat() + 
    see::scale_fill_flat() +
    geom_density(kernel = "biweight", alpha = .3) + 
    facet_wrap(~Dist_type) + 
    theme_bw()
```

@@

Net, we train the model on the data and plot the posterior distributions.

```{r Two-throws modelling, include = F, echo = F, cache = T}

Two_throw_m1 <- brm(
  abspos ~ norm_delta * Num_throws + (norm_delta * Num_throws|Participant),
  family = "beta",
  data = model_data_pos,
  prior = my_prior, 
  cores = 1,
  chains = 1,
  iter = 10000,
  warmup = 5000,
  control = list(adapt_delta = .99, max_treedepth = 15))

@@

```{r}

summary(Two_throw_m1)

Does $\hat{R} = 1$? Do we have a good number of effective samples?

If so, we can have a look at the model fit...

```{r PltTwoThrowEstimates, include = T, echo = F, fig.asp=.55, fig.cap="_The top plots show the Posterior distributions for the estimated mean standing position. The bottom plot shows the distribution of estimated difference between the two conditions for three difference distances_"}

# example distributions 
plt_examples <- draws$Plots[1][[1]][["data"]] %>% 
  mutate(Dist_Type = factor(Dist_type, c("Close", "Mid", "Far")),
         Num_Throws = ifelse(Num_throws == "One_throw", "One", "Two")) %>% 
  ggplot(aes(prop, 
             colour = Num_Throws,
             fill = Num_Throws)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  facet_wrap(~Dist_Type) + 
  theme_bw() + 
  scale_x_continuous(expression(Delta)) + 
  coord_cartesian(expand = F) + 
  guides(fill = guide_legend(title = "No. Throws"),
         colour = guide_legend(title = "No. Throws"))
